Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence

### 2020-07-16 drafts/outline.tex
working on methods

\documentclass[10pt,a4paper]{article}

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

@@

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{xcolor}

@@

\section{Introduction}

@@

\section{Methods}

\subsection{Theoretical Background}

@@

\marginpar{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}

\begin{figure}[h]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption{Particle capture efficiency diagram (TODO: caption)}
\end{figure}

@@

\subsection{Suspended Particle Concentration Model}
\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}

@@

\subsection{Experimental Methods}
\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}

\subsubsection{Materials}

@@

We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel. The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream and downstream edges of the well were covered with attached, flat, rectangular pieces of aluminum in order to avoid irregularities in the channel's cross-sectional shape. Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.

\begin{figure}[h]
\includegraphics[width=10cm]{wf5-200sizedist.png}
\centering
\caption{Walnut shell particle size distribution (TODO: caption, crop out previous caption)}
\end{figure}

\subsubsection{Particle Concentration Run Protocols}

\subsubsection{Flow Characterization Run Protocols}

\subsection{Statistical Analysis}

\section{Results}

@@

\section{Discussion}

>>>>

\documentclass[parskip=full-]{scrreprt}

@@

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{xcolor}
\usepackage{geometry}

\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily}

@@

\chapter{Introduction}

@@

\chapter{Methods}

\section{Theoretical Background}

@@

\begin{figure}[htbp]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \marginnote{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}[-5cm]}
\end{figure}

@@

\section{Suspended Particle Concentration Model}

@@

\section{Experimental Methods}

\subsection{Materials}

@@

We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel. The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-sectional shape. Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.

\begin{figure}[htbp]
\includegraphics[width=10cm]{wf5-200sizedist.png}
\centering
\caption{Walnut shell particle size distribution (TODO: caption, crop out previous caption)}
\end{figure}

\subsection{Particle Concentration Run Protocols}

\subsection{Flow Characterization Run Protocols}

\section{Statistical Analysis}

\chapter{Results}

@@

\chapter{Discussion}
